---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# discrete

The goal of discrete is to ...

## Installation

You can install discrete from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("hypertidy/discrete")
```



# required components

## TILING

logic: 

- file has native tiling, reported by vapour::raster_info
- file has standard line-fall-back (can it be different?)
 -- create a default tiling, standard size or 
-[ ] line is a fall back, might have internal tiling
-[ ] or impose an arbitrary one
-[ ] needs index-alignment, tiling done in index space, converted to sf

## POLYGONS
-[x] non-raster conversion to sf from extent/dims
-[ ]

## EXTENT / BBOX
-[x] a "discrete" class which is xmin, ymin, xmax, ymax, nx, ny
-[x] conversion of GDAL 6-figure transform to "discrete"
-[ ] tile index conversion to cell edge, so c(offsetX, offsetY, windowX, windowY) <-> c(xmin, ymin, xmax, ymax)
-[ ] spatial extent <-> index extent, based on "discrete"


## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
#f <- head(raadtools::sstfiles()$fullname, 1)
f <- 'NETCDF:"/rdsi/PUBLIC/raad/data/eclipse.ncdc.noaa.gov/pub/OI-daily-v2/NetCDF/1981/AVHRR/avhrr-only-v2.19810901.nc":sst'
#f <-  "/rdsi/PUBLIC/raad/data/www.ngdc.noaa.gov/mgg/global/relief/ETOPO2/ETOPO2v2-2006/ETOPO2v2c/netCDF/ETOPO2v2c_f4.nc"
library(vapour)
ri <- raster_info(f)
library(sf)
tiles <- tile_gon(transform6(ri$geotransform, ri$dimXY/240))


tiles$raster_data <- populate_raster(nrow(tiles))
library(spex)
extent <- function(x, ...) UseMethod("extent")
extent.sfc_POLYGON <- function(x, ...) raster::extent(attr(x, "bbox")[c("xmin", "xmax", "ymin", "ymax")])

itile <- 1
library(sf)
gs <- gdal_source(r, st_geometry(tiles[itile, ]))
library(vapour)
tiles$raster_data <- populate_raster(nrow(tiles), a$tile, raster_io(f, c(gs, c(diff(gs[c(1, 3)])+1, diff(gs[c(2, 3)])+1))))
tiles$tile <- seq_len(nrow(tiles))
par(mfrow = c(2, 1))
plot(crop(r, tiles[itile, ]), asp = "")
plot(tiles$raster_data[[itile]]$data, pch = ".")


library(mapedit)
a <- selectFeatures(tiles)
gs <- gdal_source(r, st_geometry(a))
tiles$raster_data <- populate_raster(nrow(tiles), a$tile, raster_io(f, c(gs, c(diff(gs[c(1, 3)])+1, diff(gs[c(2, 3)])+1))))
par(mfrow = c(2, 1))
plot(crop(r, tiles[itile, ]), asp = "")
plot(tiles$raster_data[[a$tile]]$data, pch = ".")




```
